### 2018-11-30 manuscript/manuscript.rmd
flushing out errors

@@

partition_map_global = 
	read_tsv("../reconciliation/blast/graphs/diamond_partition_clusters.tsv") %>%
	dplyr::rename(partition=partition_name) %>%
	dplyr::rename(matrix=dataset) %>% 
	dplyr::rename(gene=cluster_number)

@@

msas = lapply(
	phylip_file_names,
	function( phylip_file ){
		print(phylip_file)
		partition_file = sub( "phy$", "nex", phylip_file )

@@

		msa = 
			PartitionedMultipleAlignment( 
				phylip_path, 
				partition_path, 
				taxa, 
				partition_map_global=partition_map_global, 
				manuscript_name=manuscript_name, 
				matrix_name=matrix_name
			)

		return( msa )
	}
)

a_file = "../data_processed/matrices/Chang2015_Chang2015.phy"
p_file = "../data_processed/matrices/Chang2015_Chang2015.nex"
msa = 
	PartitionedMultipleAlignment( 
		a_file, 
		p_file, 
		taxa, 
		partition_map_global=partition_map_global, 
		manuscript_name="Chang2015", 
		matrix_name="Chang2015"
	)

D=clade_rects(msas[[1]])

@@

partition_clusters = 
	read_tsv( "../reconciliation/blast/graphs/diamond_partition_clusters.tsv" ) %>% 
	dplyr::rename( partition=partition_name ) %>%
	dplyr::rename( matrix=dataset ) %>%
	dplyr::rename( cluster_id=cluster_number )

@@

partition_clusters %<>% left_join( partition_to_busco_map, by=c("manuscript", "matrix", "partition") )

@@

cluster_summary =
	partition_clusters %>% 
	group_by( cluster_id ) %>% 
	summarise( 
		n_partitions = n(), 
		n_matrices= length(unique(matrix)),
		n_with_busco = sum(! is.na(BUSCO)),
		n_unique_busco = length(unique(na.omit(BUSCO)))
	)

@@

@@

Dpart = 
	read_tsv("~/Dropbox/repo/animal_root/blast/graphs/partitions_graph.tsv") %>% 
	mutate( node1 = paste(mscript1, dataset1, part1, sep = ':') ) %>% 
	mutate( node2 = paste(mscript2, dataset2, part2, sep = ':') )

>>>>

focal_matrices = 
	read.table(text = 
		"manuscript matrix
		 Borowiec2015	Total1080
		 Chang2015 Chang2015
     Dunn2008  Dunn2008
		 Hejnol2009 Hejnol2009
		 Moroz2014 ED3a
		 Nosenko2013 nonribosomal_9187_smatrix
		 Nosenko2013 ribosomal_11057_smatrix
		 Philippe2009	Philippe2009
		Ryan2013	est.opisthokonta
		Ryan2013  genome.opisthokonta
	Simion2017	supermatrix_97sp_401632pos_1719genes
Whelan2015	Metazoa_Choano_RCFV_strict

		 ", 
 		header = TRUE, 
    stringsAsFactors = FALSE)

@@

partition_map_global = 
	read_tsv("../reconciliation/blast/graphs/diamond_partition_clusters.tsv") %>%
	dplyr::rename(partition=partition_name) %>%
	#dplyr::rename(matrix=dataset) %>% 
	dplyr::rename(gene=cluster_number)

@@

sequence_matrices = lapply(
	phylip_file_names,
	function( phylip_file ){
		print(phylip_file)
		partition_file = sub( "phy$", "nex", phylip_file )

@@

		sequence_matrix = 
			PartitionedMultipleAlignment( 
				phylip_path, 
				partition_path, 
				taxa, 
				partition_map_global=partition_map_global, 
				manuscript_name=manuscript_name, 
				matrix_name=matrix_name
			)

		return( sequence_matrix )
	}
)

D=clade_rects(sequence_matrices[[1]])

@@

@@

partition_map_global %<>% left_join( partition_to_busco_map, by=c("manuscript", "matrix", "partition") )

@@

cluster_summary =
	partition_map_global %>% 
	group_by( gene ) %>% 
	summarise( 
		n_partitions = n(), 
		n_matrices= length(unique(matrix)),
		n_with_busco = sum(! is.na(BUSCO)),
		n_unique_busco = length(unique(na.omit(BUSCO)))
	)

@@

matrix_overlap = 
	lapply(sequence_matrices, function(x) lapply(sequence_matrices, function(y) matrix_overlap(x,y))) %>% 
	unlist(recursive=FALSE) %>% 
	bind_rows()

# Remove reciprocal comparisons and comparisons to self
n = nrow(matrix_overlap)
mask = lower.tri(matrix(1:n^2, n, n))
dim(mask) = NULL
matrix_overlap = matrix_overlap[mask,]

@@

Dpart = 
	read_tsv("../reconciliation/blast/graphs/partitions_graph.tsv") %>% 
	mutate( node1 = paste(mscript1, dataset1, part1, sep = ':') ) %>% 
	mutate( node2 = paste(mscript2, dataset2, part2, sep = ':') )
